Measuring security performance in the Android ecosystem

### 2015-06-04 dastats.tex
./update.sh plus manual forward ports

\newcommand{\daEndDate}{2015-05-26}

@@

\newcommand{\daNumSigOperators}{15}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{$0.771 \pm 2.66e$}
\newcommand{\daUpdatednessNominal}{0.0512}
\newcommand{\daUpdatedness}{$0.0512 \pm 0.0002$}
\newcommand{\daUpdatednessPercNominal}{5.12\%}
\newcommand{\daUpdatednessPerc}{$5.12 \pm 0.02\%$}

@@

\newcommand{\daSecurityScoreNominal}{2.53}
\newcommand{\daSecurityScore}{$2.53 \pm 0.00$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{87.1\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$87.1 \pm 0.1\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{87\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$87 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{12.9\%}
\newcommand{\daCurrentMeanSecurityPerc}{$12.9 \pm 0.1\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{13\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$13 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.129}
\newcommand{\daCurrentVulnFree}{$0.129 \pm 0.001$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.209 \pm 9.49e$}
\newcommand{\daCurrentUpdatednessNominal}{0.0329}
\newcommand{\daCurrentUpdatedness}{$0.0329 \pm 0.0008$}
\newcommand{\daCurrentUpdatednessPercNominal}{3.29\%}
\newcommand{\daCurrentUpdatednessPerc}{$3.29 \pm 0.08\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{3.3\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$3.3 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.3}
\newcommand{\daCurrentSecurityScore}{$3.3 \pm 0.0$}

@@

\newcommand{\daNumFullVersionUpdates}{4\,520}

@@

\newcommand{\daOSCurveFitParamFirst}{85.0}

@@

\newcommand{\daOSCurveHalfDeployedYearsNominal}{0.887}
\newcommand{\daOSCurveHalfDeployedYears}{$0.887 \pm 0.248$}

@@

\newcommand{\daAPICurveHalfDeployedYears}{$0.934 \pm 0.242$}

@@

\newcommand{\daAPICurveFullDeployedNominal}{1\,130}
\newcommand{\daAPICurveFullDeployed}{$1\,130 \pm 256\,000$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.20 \pm 0.00$ & $0.32 \pm 0.00$ & $0.88 \pm 0.00$ & $3.51 \pm 0.01$ \\  Motorola & $0.17 \pm 0.00$ & $0.12 \pm 0.00$ & $1.10 \pm 0.01$ & $2.57 \pm 0.01$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.88 \pm 0.00$ & $2.39 \pm 0.00$ \\  asus & $0.19 \pm 0.00$ & $0.52 \pm 0.01$ & $21.42 \pm 0.09$ & $2.30 \pm 0.02$ \\  Sony & $0.13 \pm 0.00$ & $0.19 \pm 0.00$ & $1.68 \pm 0.01$ & $2.04 \pm 0.01$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & $1.40 \pm 0.00$ & $2.02 \pm 0.01$ \\  other & $0.06 \pm 0.00$ & $0.04 \pm 0.00$ & $1.77 \pm 0.00$ & $1.25 \pm 0.00$ \\  Symphony & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $15.00 \pm 0.03$ & $0.24 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $20.79 \pm 0.06$ & $0.23 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.51}
\newcommand{\daSecScoreBestmanufacturerScore}{$3.51 \pm 0.01$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{130}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.235}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.235 \pm 0.007$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.51 \pm 0.00$ & $0.55 \pm 0.01$ & $2.18 \pm 0.02$ & $4.29 \pm 0.03$ \\  Nexus 4 & $0.28 \pm 0.00$ & $0.82 \pm 0.01$ & $21.70 \pm 0.12$ & $3.58 \pm 0.04$ \\  Nexus 7 & $0.24 \pm 0.00$ & $0.74 \pm 0.01$ & $20.68 \pm 0.11$ & $3.16 \pm 0.04$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.47 \pm 0.01$ & $2.78 \pm 0.02$ \\  other & $0.09 \pm 0.00$ & $0.14 \pm 0.00$ & $0.77 \pm 0.00$ & $2.68 \pm 0.00$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $2.44 \pm 0.03$ & $1.88 \pm 0.03$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.02$ & $1.75 \pm 0.03$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $2.08 \pm 0.01$ & $1.59 \pm 0.01$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $4.70 \pm 0.03$ & $1.04 \pm 0.02$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $23.21 \pm 0.04$ & $0.57 \pm 0.01$ \\  GT-I9505 & $0.01 \pm 0.00$ & $0.13 \pm 0.00$ & $26.96 \pm 0.08$ & $0.43 \pm 0.01$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $3.17 \pm 0.03$ & $0.28 \pm 0.02$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $27.81 \pm 0.11$ & $0.24 \pm 0.02$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $6.23 \pm 0.03$ & $0.01 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $66.00 \pm 0.19$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{4.29}
\newcommand{\daSecScoreBestmodelScore}{$4.29 \pm 0.02$}

@@

\newcommand{\daSecScoreWorstmodelScoreNominal}{1.3e-28}
\newcommand{\daSecScoreWorstmodelScore}{$1.3e-28 \pm 0.0276$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.37 \pm 0.00$ & $0.47 \pm 0.00$ & $0.82 \pm 0.00$ & $4.75 \pm 0.01$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & $0.77 \pm 0.00$ & $2.37 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.26 \pm 0.00$ & $0.12 \pm 0.00$ & $0.51 \pm 0.01$ & $3.65 \pm 0.02$ \\  T-Mobile & $0.21 \pm 0.00$ & $0.18 \pm 0.00$ & $0.54 \pm 0.01$ & $3.56 \pm 0.02$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & $0.48 \pm 0.01$ & $3.39 \pm 0.02$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.51 \pm 0.01$ & $3.31 \pm 0.02$ \\  3 & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.70 \pm 0.01$ & $2.99 \pm 0.02$ \\  AT\&T & $0.12 \pm 0.00$ & $0.08 \pm 0.00$ & $0.54 \pm 0.01$ & $2.94 \pm 0.01$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.13 \pm 0.00$ & $0.73 \pm 0.01$ & $2.88 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $1.22 \pm 0.00$ & $2.40 \pm 0.01$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $1.27 \pm 0.01$ & $2.30 \pm 0.01$ \\  n Telenor & $0.03 \pm 0.00$ & $0.12 \pm 0.00$ & $1.86 \pm 0.00$ & $1.29 \pm 0.01$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $2.42 \pm 0.00$ & $0.77 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $3.26 \pm 0.02$ & $0.46 \pm 0.01$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $3.09 \pm 0.00$ & $0.41 \pm 0.00$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $4.83 \pm 0.01$ & $0.17 \pm 0.01$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.65}
\newcommand{\daSecScoreBestoperatorScore}{$3.65 \pm 0.01$}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.172}
\newcommand{\daSecScoreWorstoperatorScore}{$0.172 \pm 0.005$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{73}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0667 & 0.0714 & 0.0 \\weight $m$ & 0.222 & 0.333 & 0.0714 & 0.0 \\weight $u$ & 0.222 & 0.133 & 0.0714 & 0.0 \\$f$ & 0.444 & 0.733 & 0.5 & 0.0 \\$m$ & 0.556 & 0.8 & 0.429 & 0.5 \\$u$ & 0.889 & 0.6 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.13 \pm 1.77$ & $-0.133 \pm 2.4$ & $-2.51 \pm 1.66$ & $-2.67 \pm 1.83$ \\weight $m$ & $-0.184 \pm 0.21$ & $-0.0255 \pm 0.313$ & $-0.35 \pm 0.21$ & $-0.387 \pm 0.209$ \\equal & $-0.0792 \pm 0.0477$ & $-0.0136 \pm 0.122$ & $-0.11 \pm 0.05$ & $-0.133 \pm 0.028$ \\weight $u$ & $-0.053 \pm 0.127$ & $-0.0154 \pm 0.239$ & $0.0196 \pm 0.0792$ & $-0.0124 \pm 0.125$ \\$u$ & $0.182 \pm 1.42$ & $-0.0309 \pm 2.03$ & $1.19 \pm 1.08$ & $1.07 \pm 1.5$ \\$f$ & $0.713 \pm 0.43$ & $0.123 \pm 1.1$ & $0.991 \pm 0.536$ & $1.2 \pm 0.2$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daMeanOutstandingVulnerabilitiesNominal}{0.771}
\newcommand{\daCurrentMeanOutstandingVulnerabilitiesNominal}{0.209}
\newcommand{\daModelHalfDeployment}{27}
\newcommand{\daModelFullDeployment}{316}
\newcommand{\daModelHalfDeploymentYears}{0.074}
\newcommand{\daModelFullDeploymentYears}{0.866}

>>>>

\newcommand{\daEndDate}{2015-05-27}

@@

\newcommand{\daNumSigOperators}{14}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{$0.549 \pm 2.46e$}
\newcommand{\daUpdatednessNominal}{0.0511}
\newcommand{\daUpdatedness}{$0.0511 \pm 0.0002$}
\newcommand{\daUpdatednessPercNominal}{5.11\%}
\newcommand{\daUpdatednessPerc}{$5.11 \pm 0.02\%$}

@@

\newcommand{\daSecurityScoreNominal}{2.83}
\newcommand{\daSecurityScore}{$2.83 \pm 0.00$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{85.9\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$85.9 \pm 0.1\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{86\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$86 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{14.1\%}
\newcommand{\daCurrentMeanSecurityPerc}{$14.1 \pm 0.1\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{14\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$14 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.141}
\newcommand{\daCurrentVulnFree}{$0.141 \pm 0.001$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.201 \pm 1.16e$}
\newcommand{\daCurrentUpdatednessNominal}{0.0322}
\newcommand{\daCurrentUpdatedness}{$0.0322 \pm 0.0007$}
\newcommand{\daCurrentUpdatednessPercNominal}{3.22\%}
\newcommand{\daCurrentUpdatednessPerc}{$3.22 \pm 0.07\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{3.2\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$3.2 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.36}
\newcommand{\daCurrentSecurityScore}{$3.36 \pm 0.00$}

@@

\newcommand{\daNumFullVersionUpdates}{4\,530}

@@

\newcommand{\daOSCurveFitParamFirst}{84.8}

@@

\newcommand{\daOSCurveHalfDeployedYearsNominal}{0.888}
\newcommand{\daOSCurveHalfDeployedYears}{$0.888 \pm 0.249$}

@@

\newcommand{\daAPICurveHalfDeployedYears}{$0.934 \pm 0.243$}

@@

\newcommand{\daAPICurveFullDeployedNominal}{1\,140}
\newcommand{\daAPICurveFullDeployed}{$1\,140 \pm 256\,000$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.20 \pm 0.00$ & $0.32 \pm 0.00$ & $0.64 \pm 0.01$ & $3.83 \pm 0.02$ \\  Motorola & $0.17 \pm 0.00$ & $0.12 \pm 0.00$ & $0.73 \pm 0.02$ & $3.03 \pm 0.02$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.63 \pm 0.00$ & $2.72 \pm 0.00$ \\  Sony & $0.13 \pm 0.00$ & $0.19 \pm 0.00$ & $1.09 \pm 0.02$ & $2.61 \pm 0.02$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & $0.89 \pm 0.01$ & $2.58 \pm 0.02$ \\  asus & $0.19 \pm 0.00$ & $0.52 \pm 0.01$ & $6.01 \pm 0.07$ & $2.31 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.04 \pm 0.00$ & $1.04 \pm 0.01$ & $1.94 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & $5.00 \pm 0.04$ & $0.27 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $5.96 \pm 0.08$ & $0.25 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.83}
\newcommand{\daSecScoreBestmanufacturerScore}{$3.83 \pm 0.02$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{131}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.251}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.251 \pm 0.007$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.51 \pm 0.00$ & $0.55 \pm 0.01$ & $1.53 \pm 0.04$ & $4.74 \pm 0.04$ \\  Nexus 4 & $0.28 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.59 \pm 0.04$ \\  Nexus 7 & $0.24 \pm 0.00$ & $0.74 \pm 0.01$ & $5.92 \pm 0.09$ & $3.18 \pm 0.04$ \\  other & $0.09 \pm 0.00$ & $0.14 \pm 0.00$ & $0.55 \pm 0.00$ & $2.98 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.39 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $1.59 \pm 0.05$ & $2.42 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.28 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.75 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.25 \pm 0.04$ & $0.58 \pm 0.01$ \\  GT-I9505 & $0.01 \pm 0.00$ & $0.13 \pm 0.00$ & $6.82 \pm 0.07$ & $0.44 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.05 \pm 0.05$ & $0.27 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.91 \pm 0.08$ & $0.25 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{4.74}
\newcommand{\daSecScoreBestmodelScore}{$4.74 \pm 0.04$}

@@

\newcommand{\daSecScoreWorstmodelScoreNominal}{0.0001}
\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0276$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.37 \pm 0.00$ & $0.47 \pm 0.00$ & $0.59 \pm 0.01$ & $5.06 \pm 0.02$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & $0.55 \pm 0.00$ & $2.66 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.26 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.84 \pm 0.03$ \\  T-Mobile & $0.21 \pm 0.00$ & $0.18 \pm 0.00$ & $0.42 \pm 0.02$ & $3.73 \pm 0.03$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & $0.39 \pm 0.03$ & $3.52 \pm 0.04$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.40 \pm 0.02$ & $3.46 \pm 0.03$ \\  3 & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.52 \pm 0.03$ & $3.23 \pm 0.04$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.13 \pm 0.00$ & $0.50 \pm 0.03$ & $3.18 \pm 0.04$ \\  AT\&T & $0.13 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.09 \pm 0.02$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.83 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $0.87 \pm 0.02$ & $2.80 \pm 0.02$ \\  n Telenor & $0.03 \pm 0.00$ & $0.12 \pm 0.00$ & $1.25 \pm 0.02$ & $1.81 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.62 \pm 0.03$ & $1.28 \pm 0.03$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.08 \pm 0.04$ & $0.90 \pm 0.03$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.03 \pm 0.02$ & $0.85 \pm 0.01$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.61 \pm 0.04$ & $0.54 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.84}
\newcommand{\daSecScoreBestoperatorScore}{$3.84 \pm 0.02$}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.535}
\newcommand{\daSecScoreWorstoperatorScore}{$0.535 \pm 0.017$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{71}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0 & 0.0714 & 0.0 \\weight $m$ & 0.222 & 0.333 & 0.143 & 0.0 \\$f$ & 0.444 & 0.733 & 0.429 & 0.0 \\weight $u$ & 0.444 & 0.133 & 0.214 & 0.0 \\$m$ & 0.667 & 0.733 & 0.357 & 0.5 \\$u$ & 0.778 & 0.733 & 0.714 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.9 \pm 2.2$ & $-0.666 \pm 2.51$ & $-3.27 \pm 1.39$ & $-3.37 \pm 1.83$ \\weight $m$ & $-0.295 \pm 0.274$ & $-0.102 \pm 0.316$ & $-0.458 \pm 0.177$ & $-0.487 \pm 0.209$ \\equal & $-0.116 \pm 0.065$ & $-0.039 \pm 0.113$ & $-0.146 \pm 0.049$ & $-0.166 \pm 0.028$ \\weight $u$ & $-0.0526 \pm 0.127$ & $-0.0152 \pm 0.239$ & $0.02 \pm 0.07$ & $-0.012 \pm 0.125$ \\$u$ & $0.516 \pm 1.61$ & $0.198 \pm 2.14$ & $1.51 \pm 0.96$ & $1.38 \pm 1.5$ \\$f$ & $1.04 \pm 0.58$ & $0.351 \pm 1.02$ & $1.31 \pm 0.44$ & $1.5 \pm 0.2$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daMeanOutstandingVulnerabilitiesNominal}{0.549}
\newcommand{\daCurrentMeanOutstandingVulnerabilitiesNominal}{0.201}
\newcommand{\daModelHalfDeploymentYears}{0.0822}
\newcommand{\daModelHalfDeployment}{30}
\newcommand{\daModelFullDeploymentYears}{0.89}
\newcommand{\daModelFullDeployment}{325}
